\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage[english]{babel} 

\makeatletter
\adddialect\l@ENGLISH\l@english
\makeatother

% ***GRAPHIC PACKAGES ***
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,backgrounds,calc}
\usepackage{multirow}
%"arrows", "automata", "backgrounds", "calendar", "chains", "matrix", "mindmap", "patterns", "petri", "shadows", "shapes.geometric", "shapes.misc", "spy", "trees".
%\usetikzlibrary{⟨list of libraries separated by commas⟩}

% *** CITATION PACKAGES ***
\usepackage{cite}

% *** MATH PACKAGES ***
\usepackage[cmex10]{amsmath}
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
\usepackage{algorithm} 
%\usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\usepackage{ marvosym } % @ symbol \MVAt
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html

% *** ALIGNMENT PACKAGES ***
\usepackage{array}
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

\usepackage{mdwmath}
\usepackage{mdwtab}
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUB+FIGURE PACKAGES ***
\usepackage{wrapfig}
\usepackage{float}
%\usepackage[tight,footnotesize]{subfigure}
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
\usepackage[font=footnotesize]{subfig}
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
\usepackage{fixltx2e}
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% \url{my_url_here}.

\usepackage{textcomp}
% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***

% correct bad hyphenation here
\hyphenation{efficiency infra-structure electri-city}



\begin{document}

% can use linebreaks \\ within to get better formatting as desired
\title{Energy Efficiency as a Orchestration Service for the Internet of Things}

\author{\IEEEauthorblockN{Peramanathan Sathyamoorthy\IEEEauthorrefmark{1} and
Edith Ngai\IEEEauthorrefmark{2}\\}
\IEEEauthorblockA{Department of Information Technology\\
Uppsala University, Sweden\\
Email: \IEEEauthorrefmark{1}sathyam.peram@gmail.com, \IEEEauthorrefmark{2} http://user.it.uu.se/\texttildelow{eding810}}
}


% The paper headers
%\markboth{Proceedings of SNCNW, May~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Energy Efficiency as a Service for Internet of Things}

\maketitle
\pagestyle{empty}
\thispagestyle{empty}
\begin{abstract}
\input{section/abstract.tex}
\end{abstract}

\begin{IEEEkeywords}
IoT, Data Communications, Mobile Cloud Computing, Crowd Sourcing , Energy Efficiency, Orchestration
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}
\input{section/intro.tex}
\section{Related Work}
\input{section/bg.tex}
\section{Cloud Orchestration for Energy Efficiency}
\input{section/Orch.tex}
\section{Preliminary investigations}
\input{section/preinvres.tex}
\section{Conclusion}
\input{section/conclusion.tex}

%\appendices
%\section{Trepn Profiler for Eclipse}
%

% use section* for acknowledgement
\section*{Acknowledgment}
We would like to thank our reviewers for their valuable comments and the work is supported by the project with Ericsson through SSF Mobility grant.

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\begin{thebibliography}{9}
\bibitem{IoT:Defn}
J. Gubbi, R. Buyya, S. Marusic, and M. Palaniswami, “Internet of Things (IoT): A vision, architectural elements, and future directions,” Future Generation Computer Systems, vol. 29, no. 7, pp. 1645–1660, Sep. 2013.
\bibitem{IoT:Challenge}
J. Chase, The Evolution of the Internet of Things. Dallas, TX: Texas Instruments Incorporated, 2013.
\bibitem{BigD:Deep}
M. M. Najafabadi, F. Villanustre, T. M. Khoshgoftaar, N. Seliya, R. Wald, and E. Muharemagic, “Deep learning applications and challenges in big data analytics,” Journal of Big Data, vol. 2, no. 1, Feb. 2015.

\bibitem{IEA:bdle}
International Energy Agency, "More Data, Less Energy - Making Network Standby More Efficient in Billions of Connected Devices" \copyright OECD/IEA, 2014 Licence:\url{https://www.iea.org/t&c/termsandconditions/}

\bibitem{EE:MCCarch}
A. Tzanakaki, M. P. Anastasopoulos, S. Peng, B. Rofoee, Y. Yan, D. Simeonidou, G. Landi, G. Bernini, N. Ciulli, J. F. Riera, and others, “A converged network architecture for energy efficient mobile cloud computing,” in Optical Network Design and Modeling, 2014 International Conference on, 2014, pp. 120–125.

\bibitem{EE:JVM}
T. K. Kundu and K. Paul, “Improving Android Performance and Energy Efficiency,” 2011, pp. 256–261.

\bibitem{EE:eTime}
P. Shu, F. Liu, H. Jin, M. Chen, F. Wen, and Y. Qu, “eTime: energy-efficient transmission between cloud and mobile devices,” in INFOCOM, 2013 Proceedings IEEE, 2013, pp. 195–199.

\bibitem{EE:Multinets}
S. Nirjon, A. Nicoara, C.-H. Hsu, J. Singh, and J. Stankovic, “Multinets: Policy oriented real-time switching of wireless interfaces on mobile devices,” in Real-Time and Embedded Technology and Applications Symposium (RTAS), 2012 IEEE 18th, 2012, pp. 251–260.

\bibitem{EE:Hier}
J. Tang, Z. Zhou, J. Niu, and Q. Wang, “An energy efficient hierarchical clustering index tree for facilitating time-correlated region queries in the Internet of Things,” Journal of Network and Computer Applications, vol. 40, pp. 1–11, Apr. 2014.

\bibitem{EE:Protocol}
A. Venčkauskas, N. Jusas, E. Kazanavičius, and V. Štuikys, “An Energy Efficient Protocol For The Internet Of Things,” Journal of Electrical Engineering, vol. 66, no. 1, pp. 47–52, 2015.

\bibitem{EE:GreenSW}
B. Steigerwald and A. Agrawal, “Developing green software,” Intel White Paper, vol. 9, 2011.

\bibitem{EE:Measure}
A. Pathak, Y. C. Hu, and M. Zhang, “Where is the energy spent inside my app?: fine grained energy accounting on smartphones with eprof,” in Proceedings of the 7th ACM european conference on Computer Systems, 2012, pp. 29–42.

\bibitem{IoTA:ARM}
R. Beneficiary, I. M. L. FhG, S. H. SAP, E. H. HSG, C. Jardak, A. O. CEA, A. Serbanati, M. T. SAP, and J. W. Walewski, “Internet of Things-Architecture IoT-A Deliverable D1. 3–Updated reference model for IoT v1. 5.”
\bibitem{Orches:Arch}
A. González García, M. Alvarez Alvarez, J. Pascual Espada, O. Sanjuán Martínez, J. M. Cueva Lovelle, and C. Pelayo G-Bustelo, “Introduction to Devices Orchestration in Internet of Things Using SBPMN,” International Journal of Interactive Multimedia and Artificial Intelligence, vol. 1, no. 4, p. 16, 2011.

\bibitem{IoT:Survey}
L. Atzori, A. Iera, and G. Morabito, “The Internet of Things: A survey,” Computer Networks, vol. 54, no. 15, pp. 2787–2805, Oct. 2010.
\bibitem{IoT:Arch}
H. Suo, J. Wan, C. Zou, and J. Liu, “Security in the Internet of Things: A Review,” 2012, pp. 648–651.
\bibitem{EModel}
A. Pathak, Y. C. Hu, M. Zhang, P. Bahl, and Y.-M. Wang, “Fine-grained power modeling for smartphones using system call tracing,” in Proceedings of the sixth conference on Computer systems, 2011, pp. 153–168.
\bibitem{trepn}
Qualcomm Technologies, Inc. "Trepn Profiler" \url{https://developer.qualcomm.com/mobile-development/increase-app-performance/trepn-profiler}, Apr. 15, 2015.

\end{thebibliography}

% that's all folks
\end{document}


%%%%% Additional Bibs %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Open probs and energy minimization
%\bibitem{EE:Eaware}
%B. L. A. BLA and L. A. BLA, “Fine-Grained Application Analysis for Energy-Aware Computing,” 2011.
%
%\bibitem{EE:RedunData}
%B. Fateh and M. Govindarasu, “Energy minimization by exploiting data redundancy in real-time wireless sensor networks,” Ad Hoc Networks, vol. 11, no. 6, pp. 1715–1731, Aug. 2013.
%\bibitem{EE:Diagnosis}
%A. J. Oliner, A. P. Iyer, I. Stoica, E. Lagerspetz, and S. Tarkoma, “Carat: collaborative energy diagnosis for mobile devices,” 2013, pp. 1–14.
%
%\bibitem{OpenProbs}
%T. Locher, P. Von Rickenbach, and R. Wattenhofer, “Sensor networks continue to puzzle: Selected open problems,” in Distributed Computing and Networking, Springer, 2008, pp. 25–38.


% Architecture level Energy Efficiency
%\bibitem{EE:Comm}
%S. T. Kouyoumdjieva, O. Helgason, E. A. Yavuz, and G. Karlsson, “Evaluating an energy-efficient radio architecture for opportunistic communication,” in Communications (ICC), 2012 IEEE International Conference on, 2012, pp. 5751–5756.

% Energy Measure

%\bibitem{EE:Prog}
%S. Hao, D. Li, W. G. Halfond, and R. Govindan, “Estimating mobile application energy consumption using program analysis,” in Software Engineering (ICSE), 2013 35th International Conference on, 2013, pp. 92–101.
%
%\bibitem{EE:MeasureWiFi}
%A. Rice and S. Hay, “Measuring mobile phone energy consumption for 802.11 wireless networking,” Pervasive and Mobile Computing, vol. 6, no. 6, pp. 593–606, Dec. 2010.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%